---
title: "Exchange Rates 2013-2022"
author: "Lim Zhi Chao"
date: "`r format(Sys.time(),'%B %Y')`"
output: html_document
params:
  curr: 'JPY'
  yearly: '2022' # YYYY format
  monthly: 'July' # Full name
  monthly_year: '2022' # YYYY format
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data contains exchange rates for 1 SGD from year 2013-2022. Data in the Excel file was obtained via web scrapping of [X-RATES website](https://www.x-rates.com/).
Currency and date parameters can be adjusted in the YAML header.

## Main libraries used:

1. `readxl` for importing of data
2. `dplyr` for data manipulation
3. `ggplot2` for data visualization

```{r load libraries, include=FALSE}
library(readxl)
library(tidyverse)

months=c("January","Febuary","March","April","May","June","July","August","September","October","November","December" )

```

### Importing Data

```{r importing data}

filename = "../SGD Exchange Rates 2013-2022.xlsx"
sheets = lapply( excel_sheets(filename), function(x) read_excel(filename, col_names=TRUE, sheet=x))
all_exc = list_rbind(sheets)

```

### SGD/`r params$curr` Exchange Rates

#### Extracting SGD/`r params$curr` from data

```{r extract}

# Change currency rates to numeric values and dates to character values
# Create new column with concatenated date
# Select new date column and relevant currency exchange rates
# Rename exchange rate column for ease of manipulation later
exc = all_exc %>%
  mutate_if( is.character, as.numeric ) %>%
  mutate_at( vars(c(year,month,day)), as.character ) %>%
  mutate( date = str_c( year,month,day,sep='-') ) %>%
  select( date, contains(params$curr) ) %>%
  rename_with( function(x) x=params$curr, starts_with("SGD") )

# Ordering the dates for graph plotting
exc$date = factor(exc$date, levels=exc$date )

```

#### Year of `r params$year`

```{r yearly}

# Creating axis breaks
ticks=c()
for (i in as.character(1:12)){
  ticks = c( ticks, str_c( params$yearly, i, "1", sep="-") )
}

# Filtering out relevant dates
year = exc %>%
  filter( str_detect(date,pattern=params$year) )

# Plotting of graph
ggplot( year, aes( x=date, y=.data[[params$curr]] ) ) +
  
  labs( title=str_c("SGD to ",params$curr," Exchange Rates in ",params$year),
        x="Months", y="Rates" ) +
  
  theme( axis.text.x = element_text(angle=45) ) +
  
  scale_x_discrete( breaks=ticks, labels=months ) +
  
  geom_point(size=1, alpha=0.3)

```

#### Year of `r params$monthly_year`, Month of `r params$monthly`

```{r monthly}

# Obtain numeric value of month since it is given as character in params
index = as.character(which( months == params$monthly ))
date_str = str_c( params$monthly_year, index, sep = "-" )

# Filter out relevant dates
month = exc %>%
  filter( str_detect( date, pattern=date_str) )

# Plotting of graph
ggplot( month, aes(x=date, y=.data[[params$curr]]) ) +
  
  labs( title=str_c("SGD to ",params$curr," Exchange Rates in ", str_c(params$monthly,params$monthly_year,sep=" ")), x="Days", y="Rates" ) +
  
  scale_x_discrete( breaks=month$date, labels=1:length(month$date) ) +
  
  geom_point( size=1, alpha=0.5 )+
  
  geom_line( aes(group=1) )

```